\documentclass{article}

\usepackage{listings}
\usepackage{multicol}
\usepackage{url}

\title{Homework, Week 4, part A}
\date{November 7, 2013}

\begin{document}
\maketitle{}

\paragraph{}This builds on the tester you worked on last week. This program contains a data structure that has questions and answers, and three functions, give-test (which gives the entire test), ask-question (which asks individual questions), and list-answers (which lists individual choices for the multiple choice.)

\paragraph{}Write a new function that takes a correct answer as an argument, asks the student to enter his answer, compares the student's response with the correct answer, and return 1 if the answers match, 0 otherwise. My function is below. You are allow to peek if you can't figure it out, but try your best before you peek.  Here is the output for the function I wrote. Note the return value for the correct and incorrect answers.

\lstset{language=Lisp,numbers=left,keepspaces=false,basicstyle=\small,numberstyle=\tiny,breaklines=true,showstringspaces=false}
\begin{lstlisting}
[5]> (get-answer "George Washington")
Enter your answer: George III
The correct answer is: George Washington
0
[6]> (get-answer "George Washington")
Enter your answer: George Washington
Correct
1
\end{lstlisting}

\paragraph{}Here is my function. Notice how I use \texttt{(cond)}. I can't use \texttt{(if)} because each branch does two things --- prints text and returns a value.

\lstset{language=Lisp,numbers=left,keepspaces=false,basicstyle=\small,numberstyle=\tiny,breaklines=true,showstringspaces=false}
\begin{lstlisting}
;; get-answer from student
;; returns 1 if answer is correct, 0 otherwise
(defun get-answer (correct)
  (format t "Enter your answer: ")
  (let ((answer (read-line)))
    (cond 
      ((string-equal correct answer) (format t "~%Correct~%") 1)
      (t (format t "~%The correct answer is: ~a~%" correct) 0))))
\end{lstlisting}

\end{document}
